---
title: "Association Analysis using R"
author: "Maher Daoud"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: HPSTR 
    highlight: github
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

In this article, we will learn how to check if there is a relationship between
two variables using R, the two variables could be numerical, nominal or ordinal variables.
For this matter, I will use `kc_house_data` dataset which refers to **House Sales in King County, USA**.
Before we start, let's import kc_house_data dataset into R environment using the below code

```{r warning=FALSE}
library(MAVE)
data(kc_house_data)
df <- MAVE::kc_house_data
knitr::kable(head(df[1:6]))
```

Now, we need to select a set of columns to be used in our examples:

```{r}
df <- df[c("id", "price", "bedrooms", "sqft_living", "floors", "waterfront",
           "condition", "grade", "sqft_above", "sqft_basement", "yr_built")]
```

Where:

* id
* price: Price of the sold house, **the target** variable
* bedrooms: Numer of Bedrooms
* sqft_living: Square footage of the living room
* floors: Total floors in the house
* waterfront: Whether the house has a view a waterfront(1: yes, 0: not)
* condition: Building condition (ordered categorical variable in the range 1 - 5)
* grade: Construction quality of improvements (ordered categorical variable in the range 1 - 13)
* sqft_above: Square footage of house apart from basement
* sqft_basement: Square footage of the basement
* yr_built: Built year

After importing the data and selecting the fields, we have to change the type for each column to a proper type.

```{r}
df$price <- as.numeric(df$price)
df$bedrooms <- factor(df$bedrooms, ordered = TRUE, levels = c(0,1,2,3,4,5,6,7,8,9,10,11,33)) 
df$sqft_living <- as.numeric(df$sqft_living)
df$floors <- factor(df$floors, ordered = TRUE, levels = c(1.0,1.5,2.0,2.5,3.0,3.5)) 
df$waterfront <- factor(df$waterfront, ordered = FALSE, levels = c(0,1)) 
df$condition <- factor(df$condition, ordered = TRUE, levels = c(1,2,3,4,5)) 
df$grade <- factor(df$grade, ordered = TRUE, levels = c(1,3,4,5,6,7,8,9,10,11,12,13)) 
df$sqft_above <- as.numeric(df$sqft_above)
df$sqft_basement <- as.numeric(df$sqft_basement)
df$yr_built <- factor(df$yr_built, ordered = TRUE, levels = sort(unique(df$yr_built))) 
```

Now, we can start with the first example about association analysis using R

**1. Normal Distribution Numerical variable VS Normal Distribution Numerical variable**

We need to test if there is Monotonic relationship, Linear relationship or non-Linear relationship.

> Linear relationships are monotonic, but not all monotonic relationships are linear.
>
>* Monotonic variables increase (or decrease) in the same direction, but not always at the same rate.
>* Linear variables increase (or decrease) in the same direction at the same rate.

First we need to define the dependent and independent variables in R with the below code

## Styles

Currently `html_pretty` supports three page themes, `cayman` (the default),
`tactile`, and `architect`. And there are also two syntax highlight styles:
`github` to mimic the syntax highlight on Github, and `vignette` that is used by
`html_vignette`. If no highlight parameter is given, the default style created
by Pandoc will be used.

The theme and highlight styles can be given in the document metadata,
for example:

```yaml
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
```

## Happy Knitting!

Feel free to use the `knitr` infrastructure with dozens of tunable options in
your package vignette.

```{r fig.width=6, fig.height=6, fig.align='center'}
set.seed(123)
n <- 1000
x1  <- matrix(rnorm(n), ncol = 2)
x2  <- matrix(rnorm(n, mean = 3, sd = 1.5), ncol = 2)
x   <- rbind(x1, x2)
head(x)
smoothScatter(x, xlab = "x1", ylab = "x2")
```

You can also include code snippets of languages other than R, but note that
the block header has no curly brackets around the language name.

```cpp
// [[Rcpp::export]]
NumericVector timesTwo(NumericVector x) {
    return x * 2;
}
```

You can write math expressions, e.g. $Y = X\beta + \epsilon$,
footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(iris, 10))
```

## Stay Tuned

Please visit the [development page](http://github.com/yixuan/prettydoc/) of the 
`prettydoc` package for latest updates and news. Comments, bug reports and
pull requests are always welcome.

